% !TEX program = XeLaTeX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{article} % Document font size and paper size

\usepackage{xstring}
\usepackage{fontspec} % Allows the use of OpenType fonts

\usepackage{geometry} % Allows the configuration of document margins
\geometry{a4paper, left=45mm, top=20mm,right=20mm,bottom=30mm} % Document margin settings
\setlength\parindent{0in} % Remove paragraph indentation

\usepackage[usenames,dvipsnames]{xcolor} % Custom colors

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{fullwidth}


\usepackage{bbding}
\usepackage{wasysym}
\usepackage{fontspec}
\newcommand*{\mobilePhone}{{\fontspec{symbola.ttf}\symbol{"1F4F1}}}
\newcommand*{\clamshellMobilePhone}{{\fontspec{symbola.ttf}\symbol{"1F581}}}
\newcommand*{\phoneA}{{\fontspec{code2000.ttf}\symbol{"260E}}}
\newcommand*{\phoneB}{{\fontspec{symbola.ttf}\symbol{"260E}}}
\newcommand*{\phoneC}{{\fontspec{quivira.otf}\symbol{"260E}}}
\newcommand*{\phoneWhiteA}{{\fontspec{code2000.ttf}\symbol{"260F}}}
\newcommand*{\phoneWhiteB}{{\fontspec{symbola.ttf}\symbol{"260F}}}
\newcommand*{\phoneWhiteC}{{\fontspec{quivira.otf}\symbol{"260F}}}
\newcommand*{\phoneReceiverA}{{\fontspec{symbola.ttf}\symbol{"1F4DE}}}
\newcommand*{\phoneReceiverB}{{\fontspec{quivira.otf}\symbol{"1F4DE}}}
\usepackage{fontawesome}
\newcommand*\fanMobile{{\FA\symbol{"F10B}}}



\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\footnotesize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{15pt} % Slightly increase the distance of the margin years from the content (was 7pts)
\reversemarginpar


\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Francois Waldner - vita},pdfauthor={Franz Waldner}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information

% Tweak to sort bib in reverse order
\usepackage{etaremune}
\makeatletter
\long\def\thebibliography#1{%
  \section*{\refname}%
  \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}
  \settowidth{\dimen0}{\@biblabel{#1}}%
  \setlength{\dimen2}{\dimen0}%
  \addtolength{\dimen2}{\labelsep}
  \sloppy
  \clubpenalty 4000 
  \@clubpenalty 
  \clubpenalty 
  \widowpenalty 4000
  \sfcode `\.\@m
  \renewcommand{\labelenumi}{\@biblabel{\theenumi}} % labels like [3], [2], [1]
  \begin{etaremune}[labelwidth=\dimen0,leftmargin=\dimen2]\@openbib@code
}
\def\endthebibliography{\end{etaremune}}
\def\@bibitem#1{%
  \item \if@filesw\immediate\write\@auxout{\string\bibcite{#1}{\the\value{enumi}}}\fi\ignorespaces
}
\makeatother


\newcommand{\cvsection}[1]{
  \par\addvspace{1.5ex}
  \phantomsection{}
  \sectionstyle{#1}
  \color{gray}\vhrulefill{0.9pt}
  \par\nobreak\addvspace{1ex}
}

\usepackage{changepage}

%----------------------------------------------------------------------------------------
%	FONT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% Two font choices are available in this template, the default is Linux Libertine, available for free at: http://www.linuxlibertine.org while the secondary choice is Hoefler Text which comes bundled with Mac OSX.
% To use Hoefler Text, comment out the Linux Libertine block below and uncomment the Hoefler Text block. You will also need to replace the "\&" characters with "\amper{}" in section titles.

% Linux Libertine Font (default)
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\sectionfont{\mdseries\upshape\Large} % Set font options for sections
\subsectionfont{\mdseries\scshape\normalsize} % Set font options for subsections
\subsubsectionfont{\mdseries\upshape\large} % Set font options for subsubsections
\chardef\&="E050 % Custom ampersand character

% Hoefler Text Font (bundled with Mac OSX)
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
%\setsansfont[Scale=0.9]{Optima Regular} % Set sans font, used in the main name and titles in the document
%\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}} % Custom ampersand character
%\sectionfont{\sffamily\mdseries\large\underline} % Set font options for sections
%\subsectionfont{\rmfamily\mdseries\scshape\normalsize} % Set font options for subsections
%\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} % Set font options for subsubsections

%-------------------------------------------------------------------------------
%                Configuration for colors
%-------------------------------------------------------------------------------
% Gray-scale colors
\definecolor{white}{HTML}{FFFFFF}
\definecolor{black}{HTML}{000000}
\definecolor{darkgray}{HTML}{333333}
\definecolor{gray}{HTML}{5D5D5D}
\definecolor{lightgray}{HTML}{999999}
% Basic colors
\definecolor{green}{HTML}{C2E15F}
\definecolor{orange}{HTML}{FDA333}
\definecolor{purple}{HTML}{D3A4F9}
\definecolor{red}{HTML}{FB4485}
\definecolor{blue}{HTML}{6CE0F1}
% Text colors
\definecolor{darktext}{HTML}{414141}
\colorlet{text}{darkgray}
\colorlet{graytext}{gray}
\colorlet{lighttext}{lightgray}
% Awesome colors
\definecolor{awesome-emerald}{HTML}{00A388}
\definecolor{awesome-skyblue}{HTML}{0395DE}
\definecolor{awesome-red}{HTML}{DC3522}
\definecolor{awesome-pink}{HTML}{EF4089}
\definecolor{awesome-orange}{HTML}{FF6138}
\definecolor{awesome-nephritis}{HTML}{27AE60}
\definecolor{awesome-concrete}{HTML}{95A5A6}
\definecolor{awesome-darknight}{HTML}{131A28}
\colorlet{awesome}{awesome-red}

\hypersetup{linkcolor=graytext,citecolor=graytext,filecolor=graytext,urlcolor=awesome} % Link colors


%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{adjustwidth}{-2.4cm}{2.4cm}
\begin{minipage}[b]{1.17\textwidth}
\centering
\vspace{-0.5cm}
\hspace{-0.4cm}\resizebox{0.71\linewidth}{!}{ François \textbf{WALDNER}} \\
\vspace{0.2cm}
{\large \color{awesome} \textsc{Bioengineer $\cdot$ Remote Sensing \& GIS Specialist $\cdot$ Data Scientist}}\\
\end{minipage}% <---------------- Note the use of "%"
\end{adjustwidth}

\vspace{0.2cm}

\begin{adjustwidth}{-2.4cm}{2.4cm}
\begin{minipage}[b]{1.17\textwidth}
\centering
\small

39 Rue Philippe Baucq, 1040 Brussels, Belgium\\
%\phone ~ \texttt{+32-10-473680} | 
\fanMobile ~  \texttt{+32-472-813539} | 
\faSkype ~ \texttt{waldner.francois} | 
 \href{mailto:francois.waldner@gmail.com}{francois.waldner@gmail.com} | 
ORCiD: \texttt{0000-0002-5599-7456}
\end{minipage}% <---------------- Note the use of "%"
\end{adjustwidth}

\vspace{0.2cm}

\begin{adjustwidth}{-2.4cm}{2.4cm}
\begin{minipage}[b]{1.17\textwidth}

\small
\color{graytext}
Dr. Fran\c{c}ois Waldner is a remote sensing scientist with a research specialization in large-area crop mapping and monitoring. He has recently completed a PhD on yearly cropland mapping using high resolution satellite image time series. He also contributes to developing monitoring strategies of the locusts and grasshoppers habitats. He is driven by developing innovative techniques in line with the operational requirements of the application.  Recently, he won the Agriculture award of the Data For Development  challenge organized by Orange in collaboration with the MIT. He is also  involved in several Science policy groups and Open Science initiatives.
\end{minipage}% <---------------- Note the use of "%"
\end{adjustwidth}

%\begin{minipage}[b]{.5\textwidth}
%\raggedright
%{\hspace{-2.4cm}\Huge François \textbf{WALDNER}}\\
%\vspace{0.05cm}
%\hspace{-2.4cm}{\Large Bioengineer}\\
%\end{minipage}% <---------------- Note the use of "%"
%\begin{minipage}[b]{.5\textwidth}
%\raggedleft
% Université catholique de Louvain\\ % Your address
%Croix du Sud, \texttt{2} ‐ L7.05.16\\
%\texttt{1348}, Louvain‐la‐Neuve\\
%Belgium\\ 
%\end{minipage}

%\vspace{0.5cm}

%\begin{minipage}[t]{.5\textwidth}
%\raggedright
%\hspace{-2.4cm}Born: September 16, 1989---Uccle, Belgium\\ % Your date of birth
%\vspace{0.05cm}
%\hspace{-2.4cm}Nationality: Belgian\\ % Your nationality
%\end{minipage}% <---------------- Note the use of "%"
%\begin{minipage}[t]{.5\textwidth}
%\raggedleft
%\phone ~ \texttt{+32-10-473680}\\
%\fanMobile ~  \texttt{+32-472-813539}\\ % Your phone number
%\faSkype ~ \texttt{waldner.francois}\\ % Your fax number
%\Envelope ~ \href{mailto:francois.waldner@gmail.com}{francois.waldner@gmail.com}\\ % Your email address
%Your academic/personal website
%ORCID: \texttt{0000-0002-5599-7456}
%\end{minipage}


%------------------------------------------------


% Mother tongue: French\\
% Other language: English, Spanish, Italian and Portuguese
%------------------------------------------------

\section*{\hspace{-2.4cm}{\color{awesome}P}rofessional experiences \hrulefill}

\years{07/2012-present} \textbf{{Researcher}} at the Geomatics unit of the Earth and Life Institute--Environment, Université catholique de Louvain (UCL), Belgium.\\ \vspace{-0.6cm} % Your current or previous employment position

{\footnotesize$\cdot$ Project manager and team leader in international research projects, writing research proposal, staff management.}\\ \vspace{-0.6cm}

{\footnotesize$\cdot$ PhD thesis addressing some methodological gaps to achieve accurate yearly global cropland maps.}\\ \vspace{-0.6cm}

{\footnotesize$\cdot$ Supervision of master theses and team work through collaborative research projects.}\\ \vspace{-0.6cm}

{\footnotesize$\cdot$ Coordination of field data collection and reference data collection by crowdsourcing.}\\ \vspace{-0.6cm}

{\footnotesize$\cdot$ Communications at several international conferences and workshops.}\\ \vspace{-0.6cm}

{\footnotesize$\cdot$ Contribution to guidelines and best practices.}\\ \vspace{-0.3cm}


\years{08/2016-present} \textbf{{Remote Sensing Consultant}} at MapTailor Geospatial Consulting GbR.\\ \vspace{-0.3cm} % Your current or previous employment position



\years{10/2011-4/2012} \textbf{{Traineeship}} at UCL Geomatics, spatial integration of non-navigable streams datasets, Louvain-la-Neuve, Belgium.\\ \vspace{-0.3cm}

\years{07/2011-09/2011} \textbf{{Internship}} at the National Center for Desert Locust Control, Nouakchott, Mauritania.\\ \vspace{-0.3cm}

\years{07/2010} \textbf{{Traineeship}} at  UCL Geomatics, spatial integration of agro-environmental features, Louvain-la-Neuve, Belgium.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section*{\hspace{-2.4cm}{\color{awesome}R}esearch projects \hrulefill}

\years{2016-2017} Development of a \href{http://geoagro.icarda.org/ca/}{near real-time agricultural monitoring system} at the field level in for the Fergana Valley, Central Asia  for the International Center for Agricultural Research in the Dry Areas (ICARDA).\\ \vspace{-0.3cm}

\years{2014-2017} Cross--site projects for the \href{http://www.jecam.org/}{Joint Experiment on Crop Assessment and Monitoring}.\\ \vspace{-0.3cm}

\years{07/2012-03/2017} Improved characterization of the cropland extent at local, continental and global scales in the EU-funded framework of the  \href{http://www.geoglam-sigma.info/Pages/default.aspx}{SIGMA} (Stimulating Innovation for the Global Monitoring of Agriculture) project.\\ \vspace{-0.3cm}

\years{2015-2016} Benchmarking of cropland mapping algorithm in the framework of the ESA-funded Sentinel-2 for agriculture project.\\ \vspace{-0.3cm}

\years{2012-2016}  Crop mapping and biophysical variable retrieval from multi-sensor and multi-scale satellite time series within the EU-funded IMAGINES (Implementation of Multi-scale Agricultural Indicators Exploiting Sentinels) project.\\ \vspace{-0.3cm}

\years{2012-2013}  Improved  monitoring of winter wheat in Russia combining modelling techniques with satellite data assimilation and crop type mapping within the EU-funded MOCCCASIN (MOnitoring Crops in Continental Climates through Assimilation of Satellite INformation) project.\\ \vspace{-0.3cm}

\years{2012} Update of the sector plan of Wallonia in light of tomorrow's sustainable development challenges.




%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section*{\hspace{-2.4cm}{\color{awesome}E}ducation \hrulefill}
\years{\raggedleft2012-05/2017}\textsc{PhD} in Bioscience engineering, UCL Belgium.\\
{\small \textsc{PhD} thesis dissertation title: \textit{Yearly  cropland mapping over large areas with high resolution satellite image time series.} Supervisor: Pierre Defourny (UCL)}\\\vspace{-0.3cm}

\years{\raggedleft 10/2010}\textsc{Athens Exchange program}, \textit{Magna cum laude}, Czech Technical University, Czech republic.\\
{\small Digital signal and image processing with applications}\\\vspace{-0.3cm}


\years{\raggedleft2007-2012}\textsc{MSc} in Bioengineering with a specialization in Environmental Sciences, \textit{Magna cum laude}, UCL Belgium.\\
{\small \textsc{MSc} thesis dissertation title: \textit{Analysis of satellite image time series to monitor the habitat of the Desert Locust, \textit{Shistocerca gregaria}, Forskal, 1775 in Mauritania.}
Supervisors: Pierre Defourny (UCL) and Keith Cressman (UN FAO-AGPM)}\\

\vspace{-0.3cm}


%----------------------------------------------------------------------------------------
%	GRANTS, HONORS AND AWARDS SECTION
%----------------------------------------------------------------------------------------

\section*{\hspace{-2.4cm}{\color{awesome}G}rants, honors \& awards \hrulefill}

\years{\raggedleft2017} \textbf{Best Poster Award} at the European Space Agency WorldCover 2017 Conference. \\\vspace{-0.3cm}

\years{\raggedleft2016} \textbf{Agriculture Prize of Orange's 2016 Data for Development (\href{http://d4d.orange.com/content/download/43330/405662/version/3/file/D4Dchallenge_leaflet_A4_V2Eweblite.pdf}{D4D}) Challenge}: Genesis of millet prices in Senegal: the role of production, markets and their failures. \\\vspace{-0.3cm}

\years{\raggedleft2016} \textbf{Grant from the Bill and Melinda Gates Foundation} to carry on the research on the modelling the formation of millet prices in Senegal. \\\vspace{-0.3cm}

\years{\raggedleft2012} \textbf{CERA award} for the best MSc thesis in the field of Environmental sciences.\\\vspace{-0.3cm}

\years{\raggedleft2012} \textbf{AIALv award} for the development of AgroMOB --an integrated information system to highlight the network of the Faculty of Bioscience engineering.


%----------------------------------------------------------------------------------------
%	Personal skills SECTION
%----------------------------------------------------------------------------------------

\section*{\hspace{-2.4cm}{\color{awesome}P}ersonal skills \hrulefill}



\years{\raggedleft \textsc{Measurement equipment}} Good command of GPS and instruments to measure plant canopy biophysical variables such as LAI (Hemispherical Photography) during field data collection campaigns.\\\vspace{-0.3cm}

\years{\raggedleft \textsc{Computer skills}} \textbf{Programming}: R, Matlab, python, some familiarity with C,  basic command of HTML, PHP, javascript and, mySQL. \\
\textbf{Remote Sensing \& GIS}: ESRI ArcMap, QGIS, ENVI, eCognition\\
\textbf{Typesetting}: \LaTeX, MS Word\\

\vspace{-0.3cm} 


\years{\raggedleft \textsc{Languages}} French: Native speaker | English: Proficient user (C2)  | Spanish: Independent user (B1)   | Dutch: Independent user (B1)




\section*{\hspace{-2.4cm}{\color{awesome}E}xtracurricular activities \hrulefill}

\subsection*{\hspace{-2.4cm}Activities}
\vspace{-0.3cm}
\years{\raggedleft2015-present} \textbf{Co-founder and blogger of} \href{www.guru-gis.net}{Guru-gis}, a blog on GIS and Remote Sensing data analysis with open source softwares. \\\vspace{-0.3cm}

\years{\raggedleft2015-present} \textbf{Challenger} at the the NASA Space Apps Challenge (hackathon). Development of MappsAttack, a game app to enable crowd-sourcing of validation data for Land Cover maps. Most Inspiring Project Prize Winner of Liege’s Challenge. \\\vspace{-0.3cm}

\years{\raggedleft2014-present} \textbf{Co-founder of PhDHub}, the Belgian Network for PhD Candidates and Early-Career researchers. \\\vspace{-0.5cm}

\years{\raggedleft2014-present} \textbf{Effective member of Focus Research},  the Belgian Research Policy Group that plays an active advocacy role.  Publication of "The Research in Transition", a journal (20 000 copies) distributed in all the French-speaking universities of Belgium. \\\vspace{-0.3cm}


\years{\raggedleft2014-2015} \textbf{Effective member of EURODOC}, the European Council of Doctoral Candidates and Junior Researchers, a federation of 32 national organisations of PhD candidates. Belgian delegate at the 2015 Assembly General Meeting. Member of the   Open Access Working Group. \\\vspace{-0.3cm}

\years{\raggedleft2013-2015} \textbf{Effective member of the ACELI}, the  researchers' association of the Earth and Life Institute.\\\vspace{-0.3cm}


\years{\raggedleft2014} \textbf{Startupper at Biowaste solution}.  Elected project at the BSE Academy, an entrepreneurial incubator training program organized and certified by Impulse Brussels.


\subsection*{\hspace{-2.4cm}Other interests}
--- photography
- cycling
- gardening
- hiking
- climbing
- cooking ---

%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS SECTION
%----------------------------------------------------------------------------------------



\section*{\hspace{-2.4cm}{\color{awesome}P}ublications \& talks \hrulefill}

\subsection*{\hspace{-2.4cm}Journal articles}

\def\FormatName#1{%
  \IfSubStr{#1}{Waldner}{\textbf{#1}}{#1}%
}


\nocite{waldner2017defining, waldner2017smote,loew2017abandonment,loew2017fergana,jacques2017, low2016timely, bogaert2016information, radoux2016sentinel, waldner2016towards, lambert2016cropland, tennant2016academic, waldner2016unified, beriaux2015maize, li2015generic, matton2015automated, waldner2015operational, waldner2015automated, waldner2015land, waldner2015mapping, renier2015dynamic}



\begingroup
\renewcommand{\section}[2]{}%
\bibliographystyle{elsarticle-num-tweak}
\bibliography{bibliography}
\endgroup

%------------------------------------------------

%\subsection*{Book chapters}
%\begingroup
%\renewcommand{\section}[2]{}%

%\endgroup

% \begingroup
% \renewcommand{\section}[2]{}%
% \begin{thebibliography}{10}
% \expandafter\ifx\csname url\endcsname\relax
%   \def\url#1{\texttt{#1}}\fi
% \expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
% \expandafter\ifx\csname href\endcsname\relax
%   \def\href#1#2{#2} \def\path#1{#1}\fi

% \bibitem{Obsomer2013}
% \FormatName{V.~Obsomer}, \FormatName{N.~Titeux},\FormatName{C.~Vancutsem},\FormatName{G.~Duveiller}, \FormatName{J.-F~Pekel}, \FormatName{S.~Connor},\FormatName{P.~Ceccato}, \FormatName{M.~Coosemans},
%   \href{http://www.sciencedirect.com/science/article/pii/S0034425716301936}{{From Anopheles to Spatial Surveillance: A Roadmap Through a Multidisciplinary Challenge, Anopheles mosquitoes}}, New insights into malaria vectors, Prof. Sylvie Manguin (Ed.), (2013), ISBN: 978-953-51-1188-7, InTech,
% \newblock \href {http://www.intechopen.com/books/anopheles-mosquitoes-new-insights-into-malaria-vectors/from-anopheles-to-spatial-surveillance-a-roadmap-through-a-multidisciplinary-challenge}
%   {\path{doi:10.5772/55622}}.
% \end{thebibliography}
% \endgroup


\subsection*{\hspace{-2.4cm}Selected Reports}


\begingroup
\renewcommand{\section}[2]{}%
\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{jungers2015vers}
\FormatName{Q.~Jungers}, \FormatName{A.~Leclercq},\FormatName{P.~Neri},\FormatName{J.~Radoux}, \FormatName{F.~Waldner}, \FormatName{P.~Defourny},
  \href{http://dial.uclouvain.be/pr/boreal/object/boreal:160879}{{Vers un plan de secteur durable: l'offre en logement}},(2015), UCL, Rapport de la CPDT. 
  
  \bibitem{leclercq2015versb}
\FormatName{A.~Leclercq},\FormatName{Q.~Jungers}, \FormatName{P.~Neri},\FormatName{J.~Radoux}, \FormatName{F.~Waldner}, \FormatName{P.~Defourny},
  \href{http://dial.uclouvain.be/pr/boreal/object/boreal:160880}{{Vers un plan de secteur durable: indice de durabilit{\'e} r{\'e}sidentielle (analyse multi-crit{\`e}re)}},(2015), UCL, Rapport de la CPDT.

  \bibitem{leclercq2015versa}
\FormatName{A.~Leclercq},\FormatName{Q.~Jungers}, \FormatName{P.~Neri},\FormatName{J.~Radoux}, \FormatName{F.~Waldner}, \FormatName{P.~Defourny},
  \href{http://dial.uclouvain.be/pr/boreal/object/boreal:158871}{{Vers un plan de secteur durable: m{\'e}thodologie du mod{\`e}le}},(2015), UCL, Rapport de la CPDT.


  
\end{thebibliography}
\endgroup


\subsection*{\hspace{-2.4cm}Selected recent talks}

\years{\raggedleft21/04/2016} Invited talk entitled \textit{Advances in EO Technologies for Agricultural Monitoring} at Monitoring Food Security Threats from Space, a Crop Estimation Liaison Committee Seminar on Technologies for Quantitative Crop Estimates and Condition Reporting in Agriculture, Pretoria, South Africa.\\

\years{\raggedleft05/02/2014} Talk at the \href{https://colloque6.inra.fr/gv2m/Oral-Sessions}{Global Vegetation Monitoring and Modeling conference}, Avignon, entitled: \textit{Towards the exploitation of Sentinel-1, -2 and -3 for high resolution crop mapping along the growing season.} \\



%------------------------------------------------


%----------------------------------------------------------------------------------------
%	TEACHING SECTION
%----------------------------------------------------------------------------------------

%\section*{Teaching}

%\years{\raggedleft2015} Lecturer at the \href{http://seom.esa.int/landtraining2015/page_home.php}{6th Advanced Training Course in Land Remote Sensing} summer school organized by the European Space Agency (ESA) in Bucarest, Romania. Material for both \href{http://seom.esa.int/landtraining2015/files/Day_4/D4T1b_LTC2015_Duveiller.pdf}{theoretical} and \href{http://seom.esa.int/landtraining2015/files/Day_4/D4P1b_LTC2015_Duveiller.pdf}{practical} sessions available online.\\


%------------------------------------------------

%\section*{Service to the profession}

%Member of the Scientific committee for the ``Remote Sensing of Fluorescence, Photosynthesis and Vegetation Status'' conference that will be held on 17 - 19 January 2017 at ESA-ESRIN, Frascati, Italy. \href{http://www.flex2017.org/}{http://www.flex2017.org/}\\

%Reviewing for several journals including: \\
%Remote Sensing of Environment, Journal of Geophysical Research - Biogeosciences, IEEE Transactions on Geoscience and Remote Sensing, International Journal of Applied Earth Observation and Geoinformation, Geo:Geography and Environment, Scientific Reports and Journal of Plant Physiology.\\





\vfill{} % Whitespace before final footer

%----------------------------------------------------------------------------------------
%	FINAL FOOTER
%----------------------------------------------------------------------------------------

\begin{center}
{\scriptsize Last updated: \today\ } % Any final footer text such as a URL to the latest version of your CV, last updated date, compiled in XeTeX, etc
\end{center}

%----------------------------------------------------------------------------------------

\end{document}
